Early Observations of the Type Ia Supernova \abc:\\ Evidence for Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-08-17 doc/ms.tex
Update text to describe the t^2 fit to the early obs

As previously noted, a precise determination of the rise time, $t_\mathrm{rise}$, of SNe Ia is challenging as there may be a ``dark phase'' following explosion \citep{2014ApJ...784...85P}. Nevertheless, to be consistent with previous studies (e.g., \citealt{2011MNRAS.416.2607G}), here we find $t_\mathrm{rise} = 17.91\pm _{0.07}^{0.15}$ d based on our fit for $t_0$. We caution that this measurement may be underestimated due to the uncertain time of explosion.

>>>>

Figure \ref{fig:early_lc_fit} also shows the best-fit model while fixing $\alpha = 2$. The $f \propto t^2$ model does not match the observations. Formally, for the $\alpha = 2$ model $\chi^2 = 63.7$ with $\nu = 15$ degrees of freedom (dof), while $\chi^2 = 10.2$ with $\nu = 14$ dof for the $\alpha = 0.98$ model.

As previously noted, a precise determination of the rise time, $t_\mathrm{rise}$, of SNe Ia is challenging as there may be a dark phase following explosion \citep{2014ApJ...784...85P}. Nevertheless, to be consistent with previous studies (e.g., \citealt{2011MNRAS.416.2607G}), here we find $t_\mathrm{rise} = 17.91\pm _{0.07}^{0.15}$ d based on our fit for $t_0$. We caution that this measurement may be underestimated due to the uncertain time of explosion.
